Homeless Shelter Usage Trends and Mortality: A Correlation Analysis

### 2024-04-02 paper/paper.qmd
update abstract typo

---
title: "Homeless Shelter Usage Trends and Mortality: A Correlation Analysis"
author: 
  - Maroosh Gillani
thanks: "Code and data are available at: https://github.com/Maroosh-Gillani/homeless_mortality."
date: today
date-format: long
abstract: "This paper investigates the relationship between homeless shelter usage trends and mortality among those experiencing homelessness in Toronto. Using datasets from Open Data Toronto, I analyzed patterns of shelter occupancy and transitions alongside occurrences of death among homeless individuals on a yearly basis. The findings reveal a significant correlation between shelter use patterns such as returns to shelters, and an increased risk of mortality in those months. Understanding these correlations showcases the dynamics between shelter access, economic instability, and mortality risks faced by those experiencing homelessness in Toronto, hoping to illuminate these issues, raise awareness, and to prompt reflection on potential avenues for assisting these individuals."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Homeless Shelter Usage Trends and Mortality: A Correlation Analysis"
author: 
  - Maroosh Gillani
thanks: "Code and data are available at: https://github.com/Maroosh-Gillani/homeless_mortality."
date: today
date-format: long
abstract: "This paper investigates the relationship between homeless shelter usage trends and mortality among those experiencing homelessness in Toronto. Using datasets from Open Data Toronto, I analyzed patterns of shelter occupancy and transitions alongside occurrences of death among homeless individuals on a yearly basis. The findings reveal a significant correlation between shelter use patterns such as returns to shelters, and an increased risk of mortality in those months. Understanding these correlations showcases the dynamics between shelter access, economic instability, and mortality risks faced by those experiencing homelessness in Toronto, and helps illuminate these issues, raise awareness, and to prompt reflection on potential avenues for assisting these individuals."
format: pdf
number-sections: true
bibliography: references.bib
---
